The Power of Two Random Choices\\ \large A follow up seminar to the Parallel Algorithms lecture\footnote{Jesper Larsson Träff, lecture ``Parallel Algorithms'', 2012 winter term at TU Wien.}

### 2014-02-09 article/article.tex
fibonacci tree definition

\subsection{Analysis of the Always-go-left scheme}
\label{sec:analysis:alg}

>>>>

\subsection{Analysis of the Always-go-left scheme}
\label{sec:analysis:alg}
Similarly to Section \ref{sec:analysis:greedy}, where we used symmetric witness trees to upper-bound the probability that a bin contains too many balls when using the \emph{Greedy} scheme, we will use asymmetric witness trees to get an analogous upper bound for the \emph{Always-go-left} scheme.

With one exception, the definition of an \emph{asymmetric witness tree} is the same as the definition of a symmetric witness tree, including the definition of activation. Only its structure differs from that of a symmetric tree. An asymmetric witness tree has the same structure as a $d$-ary Fibonacci tree $T_d\left(k \right)$, which is defined as follows.
\begin{compactitem}
\item $T_d(1)$ is a single node
\item $T_d(2) = T_d(1)$  
\item For $3\leq k \leq d$, $T_d(k)$ is a tree with $k-1$ children, which are the roots of the trees $T_d(k-1),\ldots,T_d(1)$.
\item For $k>d$, $T_d(k)$ is a tree with $d$ children, which are the roots of the trees $T_d(k-1),\ldots,T_d(k-d)$.
\end{compactitem}
\todo{illustrate}

A $d$-ary asymmetric witness tree of order $L$ has the structure of the Fibonacci tree $T_d(d \cdot L+1)$ and thus has $F_d(d\cdot L + 1) \geq \Phi_d^{d\cdot L-1}$ \todo{How to get this inequality?} leaves.
